%=============================================================================
% Reconstructing the Unmappable
% A reproducible red-team methodology for interactive digital-twin synthesis of
% sensitive infrastructure from commodity tools and public imagery, validated on
% the GeoTwn platform, with an integrated countermeasure design.
%
% Author: Christopher Woodyard, Vers3Dynamics
%
% Compiles with pdfLaTeX on Overleaf using the IEEEtran document class.
% All figures are drawn with TikZ, so no external image files are required.
%=============================================================================
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts

% ---- packages -------------------------------------------------------------
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{url}
\usepackage{booktabs}
\usepackage{array}
\usepackage[hidelinks]{hyperref}
\usepackage{listings}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,shapes.geometric,fit,backgrounds}

% ---- listing style (for the code excerpts) --------------------------------
\definecolor{codegray}{gray}{0.95}
\definecolor{codekw}{RGB}{0,0,180}
\definecolor{codecomment}{RGB}{0,128,0}
\definecolor{codestr}{RGB}{163,21,21}

\lstdefinestyle{ts}{
  backgroundcolor=\color{codegray},
  basicstyle=\ttfamily\scriptsize,
  keywordstyle=\color{codekw}\bfseries,
  commentstyle=\color{codecomment}\itshape,
  stringstyle=\color{codestr},
  numbers=left, numberstyle=\tiny, numbersep=5pt,
  breaklines=true, breakatwhitespace=true, showstringspaces=false,
  frame=single, framesep=3pt, columns=fullflexible, keepspaces=true,
  tabsize=2, captionpos=b, language=Java,
  morekeywords={const,let,export,function,type,return,for,if,new,void,number,string,boolean,interface}
}
\lstset{style=ts}

% ---- shared TikZ block style ---------------------------------------------
\tikzset{
  stage/.style={draw, rounded corners=2pt, align=center, minimum width=30mm,
                minimum height=7mm, font=\scriptsize, fill=blue!5},
  io/.style={draw, align=center, minimum width=30mm, minimum height=7mm,
             font=\scriptsize\itshape, fill=gray!12},
  flow/.style={-{Latex[length=2mm]}, thick}
}

\begin{document}

\title{Reconstructing the Unmappable: A Reproducible Methodology\\
for Interactive Digital-Twin Synthesis of Sensitive\\
Infrastructure from Commodity Tools and Public Imagery}

\author{\IEEEauthorblockN{Christopher Woodyard}
\IEEEauthorblockA{\textit{Vers3Dynamics} --- Independent Security Research \& AI Red Teaming\\
Artifact: \texttt{https://github.com/topherchris420/satellite-vision-scape} \quad
Live: \texttt{https://geotwn.vercel.app/}}}

\maketitle

%=============================================================================
\begin{abstract}
Turning overhead imagery into a navigable, photoreal 3D model of a sensitive
facility was, until recently, the province of national technical means:
classified photogrammetry, analyst tradecraft, and non-commodity compute. We
report a red-team study, conducted through the author's startup Vers3Dynamics,
that measures whether this barrier still holds. Our contribution is not an
application but a \emph{reproducible methodology}: a six-stage pipeline
(reference tracing $\rightarrow$ metric coordinate mapping $\rightarrow$
procedural terrain $\rightarrow$ parametric structure synthesis $\rightarrow$
procedural texture synthesis $\rightarrow$ real-time multiview rendering) that
produces an operationally useful interactive digital twin of a
strategically significant installation using only publicly observable spatial
information and off-the-shelf web technology. To evaluate feasibility we built
\emph{GeoTwn}, an experimental platform that instantiates the pipeline for a
fictionalized signals-intelligence (SIGINT) compound and deploys it as a
static web application. GeoTwn comprises 41 parametrically modeled primary
structures across 6 classes, 35 fully synthetic procedural textures, and three
camera regimes (free-fly, first-person, cinematic), with \emph{zero} external
image or 3D assets and a single non-synthetic input: one overhead reference.
Contrary to our own expectations, no automated photogrammetry or neural
reconstruction was required---manual tracing combined with procedural synthesis
was sufficient to reach operationally useful fidelity. We characterize the
artifact quantitatively, compare its capability envelope against Google Earth,
CesiumJS, and manual imagery inspection, and argue that the principal barrier to
reconstructing such facilities is no longer reconstruction \emph{technology} but
access to public \emph{spatial information}. We close with a defense-in-depth
countermeasure design---model-integrated facility-fingerprint guards, provenance
watermarking, and geofenced generation, plus data-provider and policy
controls---and a reproducibility appendix enabling independent verification.
\end{abstract}

\begin{IEEEkeywords}
red teaming, geospatial intelligence, OSINT, digital twins, 3D reconstruction,
procedural generation, AI safety, content provenance, critical infrastructure,
responsible disclosure.
\end{IEEEkeywords}

%=============================================================================
\section{Introduction}
For most of the satellite era, a walkable 3D reconstruction of a sensitive
facility required classified pipelines and compute that did not fit on a desk. We
set out to test whether that barrier still exists. This paper reports a red-team
study run through the author's startup, Vers3Dynamics, with a deliberately blunt
research question: \emph{using only commodity software and publicly observable
spatial information, how feasible is it for a single practitioner to produce an
interactive, multiview digital twin of a strategically significant
satellite-tracking / SIGINT installation and deploy it on the open web?}

We answer the question by \emph{building} the capability and measuring it. Our
central artifact---and the primary contribution---is a \emph{reproducible
methodology}, a six-stage reconstruction pipeline (Fig.~\ref{fig:pipeline}) that
transforms a single overhead reference into a navigable digital twin without any
restricted input. To evaluate the methodology we developed an experimental
platform, \emph{GeoTwn}\footnote{Artifact:
\url{https://github.com/topherchris420/satellite-vision-scape}; live platform:
\url{https://geotwn.vercel.app/}.}, which instantiates the pipeline for a
fictionalized compound we call ``PINE VEIL,'' framed in-app as a country's
``Area 51''---a stand-in for the class of real deep-desert signals-intelligence
stations whose existence governments decline to confirm. Fictionalizing the
target is an ethical choice, not a technical one: the methodology is
target-agnostic, and it is the methodology, not any coordinate set, that
constitutes the disclosure.

Our most consequential empirical observation is negative. We expected to need
automated photogrammetry, structure-from-motion, or a neural radiance field to
reach useful fidelity. We needed none of them. \emph{Manual tracing combined with
procedural synthesis was sufficient}, which means the cheapest possible method
already clears the operational bar, and the more sophisticated methods are merely
accelerants. This reframes the security problem: reconstruction is no longer gated
by technology but by the availability of public spatial information, and that
availability is expanding while the assembly cost of the tooling collapses toward
zero.

\textbf{Contributions.}
\begin{itemize}
\item \textbf{A reproducible methodology} (Section~\ref{sec:method}) for
synthesizing operationally useful interactive digital twins of sensitive
infrastructure from a single public overhead reference and commodity web
technology, presented as a stage-by-stage pipeline defenders can recognize and
interrupt.
\item \textbf{An experimental validation platform, GeoTwn}
(Section~\ref{sec:impl}), and a quantitative characterization of the artifact
(Section~\ref{sec:eval}), including a capability comparison against Google Earth,
CesiumJS, and manual imagery inspection.
\item \textbf{A threat model} (Section~\ref{sec:threat}) that locates the risk in
the \emph{ambient availability} of the pipeline and its AI-driven acceleration.
\item \textbf{A defense-in-depth countermeasure design}
(Section~\ref{sec:counter})---model-integrated facility-fingerprint guards,
provenance watermarking, geofenced generation, data-provider controls, and policy
norms---plus a reproducibility appendix (Section~\ref{sec:repro}).
\end{itemize}

%=============================================================================
\section{Related Work}
\label{sec:related}
We situate the methodology against four bodies of work: 3D reconstruction,
geospatial platforms and open data, content provenance, and GEOINT/OSINT
practice.

\subsection{Image-based and neural 3D reconstruction}
Structure-from-motion (SfM) and multi-view stereo recover geometry from
overlapping views \cite{sfm}, and neural methods---Neural Radiance Fields
(NeRF)~\cite{nerf} and 3D Gaussian Splatting~\cite{gsplat}---synthesize photoreal
novel views from sparse captures. These techniques define the ``high end'' of the
reconstruction spectrum and require multiple viewpoints or dense imagery. Our
finding is that they are \emph{not necessary}: a methodology built from manual
tracing and procedural generation reaches operationally useful fidelity from a
single overhead reference, which makes the neural techniques an upper bound on
adversary capability rather than a prerequisite.

\subsection{Geospatial platforms, digital twins, and open data}
Interactive globe and digital-twin platforms such as Google Earth and
CesiumJS~\cite{cesium} render 3D scenes, but only where a provider has modeled or
supplied the tileset; sensitive sites are frequently omitted, degraded, or
blurred at the provider's discretion. Open imagery and data ecosystems---the
Microsoft Planetary Computer~\cite{planetary}, OpenStreetMap~\cite{osm},
OpenAerialMap~\cite{oam}, and the SpatioTemporal Asset Catalog (STAC)
metadata standard~\cite{stac}---lower the cost of \emph{obtaining} the underlying
spatial information. The gap our work exposes is that an adversary need not wait
for a provider to model a site: the methodology lets them synthesize the twin
themselves for any location with a public footprint, bypassing the provider's
editorial control entirely (Section~\ref{sec:eval}).

\subsection{Content provenance and authenticity}
The Coalition for Content Provenance and Authenticity (C2PA) defines signed,
tamper-evident content credentials~\cite{c2pa}, and robust invisible watermarking
has been studied for attributing synthetic media~\cite{watermark}. These are
central to our countermeasure design (Section~\ref{sec:counter}): they do not
prevent synthesis but make a synthetic twin \emph{attributable}, countering the
``presentation laundering'' by which a rendered scene acquires the false authority
of genuine reconnaissance.

\subsection{GEOINT and OSINT practice}
Open-source intelligence tradecraft has long reconstructed facilities by hand from
public imagery and records~\cite{osint}, and NATO and allied doctrine formalize
OSINT as an intelligence discipline~\cite{natoosint}. Our contribution to this
literature is to show that the ``by hand'' reconstruction step is now trivially
\emph{interactive and shareable}: the analyst's mental model becomes a public,
navigable web artifact, and the marginal cost of that transformation is a few
hundred lines of code.

%=============================================================================
\section{Threat Model}
\label{sec:threat}

\subsection{Adversary, resources, and goal}
We model an adversary with the resources of a single motivated individual
(Fig.~\ref{fig:threat-adv}): a consumer GPU or even integrated graphics,
free-tier hosting, publicly reachable imagery, and current open-source or SaaS
tooling. No clearance, no insider access, no export-controlled software. The goal
is a \emph{usable} twin---supporting free navigation, structure-level inspection,
diurnal and viewpoint variation, and one-click deployment---not a survey-grade
metric model.

\begin{figure}[t]
\centering
\begin{tikzpicture}[node distance=4.2mm]
\node[io]    (a) {Public overhead imagery};
\node[stage] (b) [below=of a] {Commodity open-source tools};
\node[stage] (c) [below=of b] {Single practitioner (no clearance)};
\node[stage] (d) [below=of c] {Interactive reconstruction (this pipeline)};
\node[io]    (e) [below=of d] {Public web deployment (a URL)};
\draw[flow] (a)--(b); \draw[flow] (b)--(c); \draw[flow] (c)--(d); \draw[flow] (d)--(e);
\end{tikzpicture}
\caption{Adversary pipeline. Every element is commodity; the only non-synthetic
input is public imagery, and the output is an unauthenticated public URL.}
\label{fig:threat-adv}
\end{figure}

\subsection{Why ``good enough'' is the dangerous threshold}
Intelligence value does not require centimeter accuracy. A twin that correctly
conveys \emph{layout, structure taxonomy, sight lines, approach corridors,
relative scale, and diurnal lighting} is already useful for familiarization,
briefing, mission rehearsal, influence operations, or eroding the deterrent value
of secrecy. Our evaluation (Section~\ref{sec:eval}) shows GeoTwn occupies exactly
this ``good enough'' band, which is why we treat operational sufficiency, not
photogrammetric precision, as the relevant threshold.

\subsection{The AI-acceleration trajectory}
The methodology's danger is not any single instantiation but its \emph{ambient
availability} and its trajectory under generative AI (Fig.~\ref{fig:threat-ai}).
Each manual stage in Section~\ref{sec:method} has an emerging automated
counterpart: segmentation models can propose the traced perimeter, image models
can synthesize façades, and a text prompt can request a camera tour. The vector is
lower cost, lower required skill, and higher scale.

\begin{figure}[t]
\centering
\begin{tikzpicture}[node distance=3.6mm]
\node[stage] (a) {Generative AI folds in each pipeline stage};
\node[stage] (b) [below=of a] {Automation of tracing, texturing, staging};
\node[stage] (c) [below=of b] {Lower monetary + skill cost};
\node[stage] (d) [below=of c] {Reconstruction accessible to non-experts};
\node[io]    (e) [below=of d] {Higher scale: many sites, on demand};
\draw[flow] (a)--(b); \draw[flow] (b)--(c); \draw[flow] (c)--(d); \draw[flow] (d)--(e);
\end{tikzpicture}
\caption{AI-acceleration trajectory. Automation drives the ``cost to first twin''
toward zero and generalizes the capability from experts to non-experts.}
\label{fig:threat-ai}
\end{figure}

%=============================================================================
\section{Methodology}
\label{sec:method}
We present the reconstruction pipeline (Fig.~\ref{fig:pipeline}) as a
target-agnostic, reproducible method. We describe it at the level of
\emph{technique} so that defenders can recognize and interrupt each stage; we
deliberately omit any real-world georeferencing. GeoTwn (Section~\ref{sec:impl})
is one instantiation used to validate feasibility.

\begin{figure}[t]
\centering
\begin{tikzpicture}[node distance=3.6mm]
\node[io]    (s0) {Single public overhead reference};
\node[stage] (s1) [below=of s0] {\textbf{1.} Layout extraction (manual tracing)};
\node[stage] (s2) [below=of s1] {\textbf{2.} Metric coordinate mapping};
\node[stage] (s3) [below=of s2] {\textbf{3.} Procedural terrain (analytic fBm)};
\node[stage] (s4) [below=of s3] {\textbf{4.} Parametric structure synthesis};
\node[stage] (s5) [below=of s4] {\textbf{5.} Procedural texture synthesis};
\node[stage] (s6) [below=of s5] {\textbf{6.} Real-time multiview WebGL scene};
\node[io]    (s7) [below=of s6] {Interactive digital twin (deployed)};
\draw[flow] (s0)--(s1); \draw[flow] (s1)--(s2); \draw[flow] (s2)--(s3);
\draw[flow] (s3)--(s4); \draw[flow] (s4)--(s5); \draw[flow] (s5)--(s6);
\draw[flow] (s6)--(s7);
\end{tikzpicture}
\caption{The reproducible reconstruction pipeline. The only non-synthetic input is
a single public overhead reference; every subsequent stage is procedural and
runs on commodity hardware in a web browser.}
\label{fig:pipeline}
\end{figure}

\subsection{Stage 1 --- Layout extraction by manual tracing}
The single non-synthetic input is one overhead reference. Features---security
perimeter, interior roads, and each structure footprint---are traced by hand into
coordinate lists. We emphasize this stage because it is our strongest scientific
observation: \emph{contrary to expectations, no automated photogrammetry or neural
reconstruction was required.} A human tracing perimeters against a single image,
combined with the procedural stages below, was sufficient to produce a navigable
twin exhibiting operationally useful fidelity. The implication is that the entire
high-end reconstruction literature (Section~\ref{sec:related}) is, from a
defender's perspective, an accelerant on top of an already-sufficient manual
baseline.

\subsection{Stage 2 --- Metric coordinate mapping}
Traced pixels are mapped by a fixed linear transform into a consistent metric
$XZ$ plane (meters, $Y$ up), origin near the compound center:
\[
x_{\text{world}} = (p_x - c_x)\cdot s, \qquad
z_{\text{world}} = (p_y - c_y)\cdot s ,
\]
with scale $s = 0.28$~m/px in our instantiation, giving a compound span of
$\approx \pm 170$~m. This single transform lets every downstream subsystem---mesh,
foliage, colliders, cameras---share one coordinate frame with no proprietary
format.

\subsection{Stage 3 --- Procedural terrain}
A single analytic height field, a pure function of $(x,z)$, keeps the ground mesh,
foliage placement, and the walking camera in agreement without shared state: the
fenced compound is held flat while fractional Brownian motion raises surrounding
relief. Being analytic, it needs no elevation dataset.

\subsection{Stage 4 --- Parametric structure synthesis}
The facility is expressed as a small vocabulary of parametric primitive classes
(spherical pressure tanks, hemispherical radomes, cylindrical tanks, buildings,
pipe racks, paved aprons). This vocabulary is the intelligence payload: it turns
``blobs in a photo'' into a typed inventory---an antenna field with a tank farm
and barracks. Counts and classes are quantified in Section~\ref{sec:eval}.

\subsection{Stage 5 --- Procedural texture synthesis}
Every surface is drawn at load time from seeded value noise onto an HTML canvas,
then promoted to a WebGL texture with derived normal and roughness maps. No
copyrighted or restricted imagery is embedded. Beyond avoiding licensing exposure,
this defeats naive provenance checks: the artifact carries \emph{no forensic trace
of source imagery}.

\subsection{Stage 6 --- Real-time multiview rendering}
The scene is rendered in-browser with WebGL. Three camera regimes provide the
``multiview'' capability that makes the twin operationally useful: free-fly
(overhead-to-oblique), first-person walk (eye-height, collider-constrained,
exposing ground-level sight lines a satellite never provides), and a scripted
cinematic tour. A commercial-imagery-grade post-processing chain (ambient
occlusion, HDR bloom, filmic tone mapping, an imagery-grade saturation/contrast
bump) makes the synthetic scene read as authentic reconnaissance---the step that
manufactures false authority, and thus a first-class target for the provenance
countermeasures of Section~\ref{sec:counter}.

%=============================================================================
\section{Implementation: The GeoTwn Validation Platform}
\label{sec:impl}
GeoTwn instantiates the pipeline as a single-page web application (React, Three.js
via React Three Fiber). It is the experimental apparatus by which we measure the
methodology's feasibility, not the contribution itself. We include representative
code to establish that the artifact is real and reproducible; full source is
public (Section~\ref{sec:repro}).

\textbf{Stage 1--2 (tracing + mapping).} The perimeter is a hand-traced polyline
in the metric frame:
\begin{lstlisting}[caption={Traced perimeter in the metric frame (\texttt{src/lib/site-layout.ts}).},label={lst:layout}]
// world_x = (px-605)*0.28, world_z = (py-628)*0.28
export const perimeterPath: [number, number][] = [
  [-136, -114], [-32, -114], [-32, 3], [14, 3], [14, 9],
  [144, 13], [144, 73], [29, 75], [29, 165],
  [-98, 165], [-98, 3], [-120, -33], [-139, -43],
];
\end{lstlisting}

\textbf{Stage 3 (terrain).} One analytic function serves the whole system:
\begin{lstlisting}[caption={Analytic terrain shared by mesh, foliage, and camera (\texttt{src/lib/terrain.ts}).},label={lst:terrain}]
export function terrainHeight(x: number, z: number): number {
  const eastFactor = ss(FENCE_EAST, FENCE_EAST + 90, x);
  const hills = fbm(x*0.012+10, z*0.012+4) * 38 * eastFactor;
  const ridge = Math.max(0, Math.sin((z+200)*0.004)) * 10 * eastFactor;
  const micro = fbm(x*0.04+3, z*0.04+7) * 0.4;
  return hills + ridge + micro; // + western roll term
}
\end{lstlisting}

\textbf{Stage 5 (textures).} A seeded LCG makes every texture byte-identical
across loads, so the artifact is deterministic and carries no source imagery:
\begin{lstlisting}[caption={Deterministic procedural texture core (\texttt{src/lib/site-textures.ts}).},label={lst:tex}]
function lcg(seed: number) {            // deterministic per-load noise
  let s = seed >>> 0 || 1;
  return () => (s = (s*1664525 + 1013904223) >>> 0) / 4294967296;
}
// 9 generator functions synthesize 35 textures (color + derived
// normal/roughness); zero external image assets are bundled.
\end{lstlisting}

\textbf{Stage 6 (rendering + adaptive quality).} The post chain launders
presentation, and a runtime monitor sheds expensive passes before render
resolution, so the twin sustains interactivity on commodity hardware:
\begin{lstlisting}[caption={Post-processing and adaptive-quality rig (\texttt{src/components/site/SiteScene.tsx}).},label={lst:post}]
<PerformanceMonitor onDecline={() => {        // shed AO/DoF, then DPR
  declineStage.current += 1;
  declineStage.current === 1 ? setQuality("low") : setDpr(1);
}}/>
<EffectComposer>
  {quality==="high" && <N8AO aoRadius={10} intensity={2.5}/>}
  <Bloom mipmapBlur intensity={0.55} luminanceThreshold={1.0}/>
  <ToneMapping mode={ToneMappingMode.ACES_FILMIC}/>
  <HueSaturation saturation={0.12}/>          {/* imagery-grade */}
  <BrightnessContrast contrast={0.07}/><SMAA/><Vignette/>
</EffectComposer>
\end{lstlisting}

%=============================================================================
\section{Evaluation}
\label{sec:eval}
We evaluate along three axes: (i) what the artifact \emph{is}, quantitatively;
(ii) how much operational intelligence it captures; and (iii) how its capability
envelope compares with existing tools. All counts in
Table~\ref{tab:sysvals} are measured directly from the public source tree.

\subsection{System characterization}
\begin{table}[t]
\caption{Measured characterization of the GeoTwn artifact}
\label{tab:sysvals}
\centering
\renewcommand{\arraystretch}{1.05}
\begin{tabular}{@{}lr@{}}
\toprule
\textbf{Property} & \textbf{Value} \\
\midrule
Total source (TypeScript/TSX)                 & 8{,}523 LOC \\
Reconstruction logic (excl. vendored UI, generated router) & 4{,}094 LOC \\
Core reconstruction modules (6 files)         & 1{,}923 LOC \\
Parametric structure classes                  & 6 \\
Primary modeled structures                    & 41 \\
\;\; spheres / radomes / cyl.\ tanks / buildings / pipe racks & 9 / 7 / 6 / 16 / 3 \\
Paved aprons                                   & 3 \\
Procedurally placed trees                      & 173 \\
Distinct procedural textures                   & 35 \\
Texture generator functions                    & 9 \\
External image / 3D assets bundled             & \textbf{0} \\
Non-synthetic inputs                           & 1 (overhead ref.) \\
Camera / view modes                            & 3 \\
Backend services                               & 0 (static SPA) \\
Pixel-to-world scale                           & 0.28 m/px \\
Production build                               & static SPA$^{\ddagger}$ \\
Deployment                                     & free-tier static host \\
Development effort (author est.)$^{\dagger}$    & $\approx$1 working day \\
\bottomrule
\end{tabular}
\\[2pt]
{\footnotesize $^{\dagger}$Order-of-magnitude author estimate; not instrumented.
$^{\ddagger}$No backend; a single static bundle reproducible via the build command
in Section~\ref{sec:repro}.}
\end{table}

The headline is the combination of the last several rows: an operationally useful
twin with \textbf{zero} external assets, \textbf{one} non-synthetic input, and
\textbf{no} backend, assembled in roughly a working day. The ``cost to first
twin''---not any pixel-accuracy metric---is the result that matters.

\subsection{Operational fidelity}
We assess fidelity against \emph{operational} rather than photogrammetric criteria
(Table~\ref{tab:fidelity}), because operational sufficiency is the threat
threshold (Section~\ref{sec:threat}).

\begin{table}[t]
\caption{Operational intelligence captured by the reconstruction}
\label{tab:fidelity}
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Intelligence attribute} & \textbf{Captured} & \textbf{Basis} \\
\midrule
Perimeter geometry \& gates   & Yes  & Traced polyline \\
Structure taxonomy \& counts  & Yes  & Parametric primitives \\
Relative scale \& spacing     & Yes  & Metric $XZ$ frame \\
Ground-level sight lines      & Yes  & First-person walker \\
Diurnal lighting variation    & Yes  & Day/night rig \\
Approach corridors / roads    & Yes  & Traced road network \\
\bottomrule
\end{tabular}
\end{table}

\subsection{What was deliberately \emph{not} demonstrated}
To bound the disclosure and be explicit for reviewers, Table~\ref{tab:notdemo}
lists capabilities the artifact intentionally excludes. Absent rows are either
self-imposed ethical guardrails (georeference) or irrelevant to operational use
(exact materials); none reflects a technical wall the methodology could not clear.

\begin{table}[t]
\caption{Capabilities intentionally excluded from the demonstration}
\label{tab:notdemo}
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Capability} & \textbf{Included} \\
\midrule
Exact absolute coordinates / georeference & No (withheld) \\
Interior / floor-plan structure           & No \\
Underground or buried assets              & No \\
Specific sensor / emitter locations       & No \\
Classified imagery                        & No \\
Proprietary / licensed data               & No \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Comparison with existing tools}
The natural objection is that interactive globes already exist. They do not close
this gap. Table~\ref{tab:compare} compares GeoTwn's capability envelope against
Google Earth, CesiumJS, and manual imagery inspection. The decisive row is the
last: existing platforms render a site \emph{only where a provider chose to model
it}, and sensitive facilities are precisely where providers omit or degrade
coverage. The methodology removes that dependency---an adversary self-synthesizes
the twin for any site with a public footprint, bypassing the provider's editorial
control.

\begin{table}[t]
\caption{Capability comparison (S = self-synthesized here)}
\label{tab:compare}
\centering
\setlength{\tabcolsep}{4pt}
\begin{tabular}{@{}lcccc@{}}
\toprule
\textbf{Capability} & \textbf{GeoTwn} & \textbf{G.\ Earth} & \textbf{Cesium} & \textbf{Manual} \\
\midrule
Free-fly navigation            & Yes & Yes  & Yes  & No  \\
Ground-level first-person view & Yes & Ltd. & Data & No  \\
Structure-level inspection     & Yes & No   & Data & Man.\\
Diurnal lighting control       & Yes & Ltd. & Yes  & No  \\
Self-hosted / offline          & Yes & No   & Yes  & --  \\
Works for \emph{unmodeled} sites & \textbf{Yes} & \textbf{No} & \textbf{No} & Man. \\
\bottomrule
\end{tabular}
\end{table}

%=============================================================================
\section{Discussion}
\label{sec:discussion}
The methodology reframes secrecy-by-reconstruction-difficulty as a failing control
for physical infrastructure, in the same way it long ago failed for software. Each
pipeline stage is independently commoditized, and generative AI is compressing the
chain (Fig.~\ref{fig:threat-ai}). Defenders therefore need controls that assume
reconstruction \emph{will} be attempted and focus on detection, provenance,
friction, and consequence---not on preventing the mathematically inevitable. The
comparison in Table~\ref{tab:compare} sharpens the point: the protective value of a
provider's decision \emph{not} to model a site evaporates once adversaries can
model it themselves.

%=============================================================================
\section{Countermeasures and Policy}
\label{sec:counter}
We organize defenses in three layers (Table~\ref{tab:defense}): model-integrated
guards, data-provider controls, and policy/disclosure norms. None suffices alone;
the design is defense-in-depth.

\subsection{Layer 1 --- Model-integrated guards}

\subsubsection{A facility-fingerprint generation guard}
Generative and 3D-reconstruction pipelines can be taught to recognize when they are
being steered toward sensitive-facility synthesis and to gate the request. The
signal is the \emph{co-occurrence} of the structure taxonomy (radome fields,
regular tank rows, barracks grids, a hardened perimeter) with prompt intent cues
and any georeference. Listing~\ref{lst:guard} sketches a pre-generation guard.

\begin{lstlisting}[caption={Illustrative pre-generation facility-fingerprint guard.},label={lst:guard}]
const SENSITIVE_TAXONOMY = ["radome","antenna field","sigint",
  "spherical tank farm","barracks grid","hardened perimeter"];
const INTENT_CUES = ["classified","top secret","area 51",
  "military base","surveillance station","recon"];

function facilityFingerprintScore(prompt, refImageTags) {
  const tax = SENSITIVE_TAXONOMY.filter(t => refImageTags.includes(t)).length;
  const intent = INTENT_CUES.filter(c => prompt.toLowerCase().includes(c)).length;
  const georef = /-?\d{1,3}\.\d{3,}\s*,\s*-?\d{1,3}\.\d{3,}/.test(prompt);
  return 0.5*tax + 0.4*intent + (georef ? 1.0 : 0); // co-occurrence
}
function guard(req) {
  const s = facilityFingerprintScore(req.prompt, req.refImageTags);
  if (s >= BLOCK)  return refuse(req, "sensitive-facility synthesis");
  if (s >= REVIEW) return degrade(req, {georef:false, navigable:false});
  return allow(req);
}
\end{lstlisting}

\noindent This is a speed bump, not a wall: a determined adversary can decompose
the request or self-host an open model. Its value is raising cost, catching the
careless majority, and creating an auditable refusal signal. Building a labeled
``sensitive-facility synthesis'' benchmark to measure its false-positive/negative
rates is future work (Section~\ref{sec:future}).

\subsubsection{Provenance watermarking and content credentials}
Compliant generators should emit signed C2PA content credentials~\cite{c2pa} plus
a robust invisible watermark~\cite{watermark} that survives screenshotting and
re-encoding, applied at the \emph{render} stage so even client-side WebGL twins
embed a detectable signal. This does not stop synthesis; it makes a twin
attributable and counters presentation laundering.

\subsubsection{Geofenced generation}
Where a request implies coordinates, models should consult a protected-zone policy
layer (analogous to drone no-fly geofencing) and refuse or degrade georeferenced
synthesis inside it. Private-set-intersection lets the model test membership
without learning---or leaking---the full protected catalog.

\subsection{Layer 2 --- Data-provider controls}
Imagery is the one non-synthetic input, hence a natural choke point: graduated
resolution/obfuscation applied \emph{consistently across providers}; query-pattern
telemetry (repeated high-zoom, multi-angle tasking over a protected footprint is
itself a reconnaissance signal); and licensing terms that prohibit derivative 3D
reconstruction of designated sites, giving platforms a takedown basis.

\subsection{Layer 3 --- Policy, disclosure, and red-team norms}
Facility-protection doctrine should adopt \emph{assume-reconstruction} planning; a
CVE-like channel should institutionalize coordinated disclosure of geospatial/AI
capability; agencies and providers should fund standing red-team programs that
track the ``cost to first twin'' as a living metric; and hosting platforms should
require content-credential support for photoreal geospatial renders of real
locations.

\begin{table}[t]
\caption{Countermeasures mapped to the pipeline}
\label{tab:defense}
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Pipeline stage} & \textbf{Primary countermeasure} \\
\midrule
1--2 Tracing / georeferencing & Provider obfuscation; geofenced generation; PSI \\
3--4 Terrain / structures     & Facility-fingerprint generation guard \\
5\phantom{--6} Textures       & (no source imagery to trace --- provenance shifts) \\
6\phantom{--6} Rendering      & Render-stage watermarking \\
Deploy                        & C2PA credentials; platform provenance mandates \\
\bottomrule
\end{tabular}
\end{table}

%=============================================================================
\section{Reproducibility}
\label{sec:repro}
The artifact is public to support independent verification. GeoTwn is a static
single-page application with no backend, so reproduction requires only a browser
and a Node toolchain.

\begin{itemize}
\item \textbf{Repository:} \url{https://github.com/topherchris420/satellite-vision-scape}
(branch used for this study noted in the repository). \textbf{Live platform:}
\url{https://geotwn.vercel.app/}.
\item \textbf{Runtime:} any WebGL2 browser (evaluated on current Chromium/Chrome).
No GPU beyond an integrated/consumer class is required; an adaptive-quality monitor
(Listing~\ref{lst:post}) degrades gracefully.
\item \textbf{Build toolchain:} Node.js~22.x, Bun~1.3.x (or npm); Vite~8;
TypeScript~5.8.
\item \textbf{Key dependencies:} \texttt{three}~0.185, \texttt{@react-three/fiber}~9.6,
\texttt{@react-three/drei}~10.7, \texttt{@react-three/postprocessing}~3.0,
\texttt{postprocessing}~6.39, \texttt{react}~19.2.
\item \textbf{Build \& run:} \texttt{bun install \&\& bun run build} (production)
or \texttt{bun run dev} (local). Output is a static bundle deployable to any
static host.
\item \textbf{Determinism:} all procedural textures and foliage use seeded
generators, so scenes are byte-reproducible across loads.
\end{itemize}

%=============================================================================
\section{Ethical Considerations and Responsible Disclosure}
\label{sec:ethics}
This work was conducted as authorized red-team research by the author's startup,
against a \emph{fictionalized} target, with absolute georeferencing deliberately
withheld (Table~\ref{tab:notdemo}). Our aim is to shorten defenders' reaction time,
not to hand adversaries a recipe for a specific site. We judge that method-level
disclosure does not meaningfully advantage a capable adversary---who can already
assemble these commodity parts---while it materially helps defenders who have not
internalized that the capability is ambient. We publish the countermeasures
(Section~\ref{sec:counter}) alongside the demonstration and welcome coordinated
contact on any element a reader believes crosses that line.

%=============================================================================
\section{Limitations and Future Work}
\label{sec:future}
GeoTwn uses manual tracing and procedural generation rather than automated neural
reconstruction; quantifying the fidelity/effort delta of an automated
NeRF/Gaussian-splat variant is open. We have not empirically measured the proposed
facility-fingerprint guard on a labeled corpus. Concrete next steps:
\begin{itemize}
\item Automatic building/structure classification from overhead references.
\item Multi-temporal satellite change detection to keep twins current.
\item Reconstruction uncertainty estimation and per-structure confidence metrics.
\item AI-assisted procedural generation to quantify the automation trajectory.
\item A public ``sensitive-facility synthesis'' benchmark for facility-fingerprint
detection, with reported false-positive/negative rates.
\item Defensive evaluation benchmarks and synthetic-data generation for standing
red-team programs.
\end{itemize}

%=============================================================================
\section{Conclusion}
This work suggests that the principal barrier to constructing interactive digital
twins of strategically significant facilities is no longer access to specialized
reconstruction technology but rather access to publicly observable spatial
information. Our reproducible six-stage methodology reaches operationally useful
fidelity from a single public overhead reference using only commodity web
technology, and our GeoTwn validation platform---41 modeled structures, 35 synthetic
textures, zero external assets, one non-synthetic input, assembled in about a
working day---demonstrates that even the cheapest reconstruction path already
clears the operational bar. As commodity, AI-assisted tooling matures,
reconstruction costs will decrease further, increasing the importance of
provenance mechanisms, policy controls, and defensive evaluation. We have proposed
a defense-in-depth response and released the artifact to support the standing
red-team programs we argue defenders now require.

\section*{Acknowledgment}
Conducted as independent security research by Vers3Dynamics. The artifact and its
source are public to support reproducibility and defensive study.

%=============================================================================
\begin{thebibliography}{00}
\bibitem{sfm} J. L. Sch\"onberger and J.-M. Frahm, ``Structure-from-Motion
Revisited,'' in \emph{IEEE CVPR}, 2016.
\bibitem{nerf} B. Mildenhall \emph{et al.}, ``NeRF: Representing Scenes as Neural
Radiance Fields for View Synthesis,'' in \emph{ECCV}, 2020.
\bibitem{gsplat} B. Kerbl, G. Kopanas, T. Leimk\"uhler, and G. Drettakis, ``3D
Gaussian Splatting for Real-Time Radiance Field Rendering,'' \emph{ACM Trans.
Graph.}, vol.~42, no.~4, 2023.
\bibitem{cesium} P. Cozzi \emph{et al.}, ``Cesium: 3D Geospatial Visualization,''
Cesium GS, Inc. [Online]. Available: \url{https://cesium.com/}
\bibitem{planetary} Microsoft, ``Planetary Computer.'' [Online]. Available:
\url{https://planetarycomputer.microsoft.com/}
\bibitem{osm} OpenStreetMap contributors, ``OpenStreetMap.'' [Online]. Available:
\url{https://www.openstreetmap.org/}
\bibitem{oam} OpenAerialMap contributors, ``OpenAerialMap.'' [Online]. Available:
\url{https://openaerialmap.org/}
\bibitem{stac} STAC contributors, ``SpatioTemporal Asset Catalog (STAC)
Specification.'' [Online]. Available: \url{https://stacspec.org/}
\bibitem{c2pa} Coalition for Content Provenance and Authenticity, ``C2PA Technical
Specification,'' 2024. [Online]. Available: \url{https://c2pa.org/}
\bibitem{watermark} S. Abdelnabi and M. Fritz, ``Adversarial Watermarking
Transformer,'' in \emph{IEEE S\&P}, 2021.
\bibitem{osint} M. Bazzell, \emph{Open Source Intelligence Techniques}, 9th ed.,
2023.
\bibitem{natoosint} NATO, ``Open Source Intelligence Handbook,'' NATO
Supreme Allied Commander Transformation, 2001.
\bibitem{threejs} Three.js contributors, ``Three.js -- JavaScript 3D Library.''
[Online]. Available: \url{https://threejs.org/}
\bibitem{r3f} Poimandres, ``React Three Fiber.'' [Online]. Available:
\url{https://docs.pmnd.rs/react-three-fiber}
\bibitem{getwn} C. Woodyard (Vers3Dynamics), ``GeoTwn / satellite-vision-scape,''
2025. [Online]. Available:
\url{https://github.com/topherchris420/satellite-vision-scape}
\bibitem{demo} C. Woodyard, ``GeoTwn live platform,'' 2025. [Online]. Available:
\url{https://geotwn.vercel.app/}
\end{thebibliography}

\end{document}
